On the error performance of the $A_n$ lattices

### 2012-03-12 paper.tex
minor edits.
minor edits

In the AWGN channel the received signal takes the form
\[
\ybf = \cbf + \wbf
\]
where $\ybf \in \reals^n$, $\cbf \in \calC$ and $\wbf$ is a vector of independent and identically distributed Gaussian random variables with variance $\sigma^2$.  If the receiver employs maximum likelihood decoding then the estimator of $\cbf$ given $\ybf$ at the receiver is
\begin{equation}\label{eq:mldecoder}
\hat{\cbf}_{\text{ML}} = \underset{\cbf \in \calC}{\operatorname{argmin}}\;\| \ybf - \cbf \|^2,
%\hat{\cbf} &=& \mbox{arg~}\min_{\cbf \in \calC} \| \ybf - \cbf \|^2.
\end{equation}
that is, the receiver computes the codeword in $\calC$ nearest in Euclidean distance to the received signal $\ybf$.  Assuming that each codeword is transmitted with equal probability, then the probability of correct maximum likelihood decoding is
\[
P_{\text{ML}} = \sum_{\cbf \in \calC}\frac{1}{\abs{\calC}}\prob( \hat{\cbf}_{\text{ML}} = \cbf ).
\]

@@

This theorem asserts that the Voronoi cell of the lattice $A_n$ is the $n$-dimensional polytope that results from orthogonally projecting the $(n+1)$-dimensional hypercube into the zero-sum plane.  Results of this type have been studied previously.  A polytope that is the orthogonal projection of a hypercube is called a \emph{zonotope}~\cite[p.~313]{surveys_combin_zonotopes_1997}~\cite{McMullen_space_tiling_zonotopes_1975}.  Figure~\ref{fig:cuberothex} depicts some 2-dimensional zonotopes.  A zonotope is \emph{unimodular} if it can be used to tile (or tessellate) Euclidean space.  Such a tessellation naturally gives rise to a lattice, a so called \emph{zonotopal lattice}~\cite{Vallentin_space_tiling_zonotope_2004}.  The lattice $A_n$ is a zonotopal lattice.  The techniques in this paper can potentially be extended to other zonotopal lattices, but we do not consider such extensions here.

@@

We have observed the following property.  The formula for $M_n(m)$ appears to always be in the form
\[
\frac{p(n)}{(1+n)^{m-1/2} d}
\] 
where $p(n) = a_0 + a_1n + \dots a_{2m} n^{2m}$ is a polynomial of order $2m$ and $d \in \ints$ is the denominator.  The following appears to be true
\[
\frac{d}{a_{2m}} = 12^m,
\]
that is, the integer on the denominator $d$ is equal to the highest order coefficient $a_{2m}$ of the numerator polynomial $p(n)$ multiplied by $12^m$.  This leads us to make the following conjecture about the moments of $A_n$ when the dimension $n$ gets large.

@@

% \section{Conclusion}
% \begin{itemize}
% \item We can use these techniques to compute other things about the Voronoi cell, i.e. the average $L_p$ norms.
% \item Not restricted to Gaussian noise.  Any noise pdf that can be described by the moments will work.
% \item Can other lattices be done?
% \end{itemize}

@@

% \section{Notable references}
% \begin{itemize}
% \item Conway and Sloane compute the second moment of all the root lattices and there duals~\cite{Conway1982VoronoiRegions}.  This is really \emph{the} paper on this topic.  The approach is to break the Voronoi cells into simplicies and compute the second moment of the simplicies.

% \begin{quotation}
% In the second application, the same Euclidean code
% $y_1,\dots ,y_n$ is used as a code for the Gaussian channel. Now
% the Voronoi regions are the decoding regions: all points $x$
% in the interior of $V(y_i)$ are decoded as $y_i$. If the codewords
% are equally likely and all the Voronoi regions $V(y_i)$ are
% congruent to a polytope P, the probability of correct decoding is proportional to
% \[
% \int_P e^{x^\prime x} dx.
% \]
% The description of the Voronoi regions given in Section III
% thus makes it possible to calculate this probability exactly
% for many Euclidean codes. These results will be described
% elsewhere.
% \end{quotation}

% But it doesn't appear to be published elsewhere.  I'm not really sure how you would go about doing it either, because I think integrating $e^{x^\prime x}$ over an arbitray simplex is hard.

% \item Baldoni \emph{et. al.}~\cite{Baldoni_how_to_integrate_poly_over_simplex_2008} claim to show that in general integrating a polynomial under a simplex is NP-hard.  However, if you fix the degree of the polynomial then it can be done in polynomial time.

% \end{itemize}

>>>>

In the AWGN channel the received signal takes the form
\[
\ybf = \cbf + \wbf
\]
where $\ybf \in \reals^n$, $\cbf \in \calC$ and $\wbf$ is a vector of independent and identically distributed Gaussian random variables with variance $\sigma^2$.  If the receiver employs maximum likelihood decoding then the estimator of $\cbf$ given $\ybf$ at the receiver is
\begin{equation}\label{eq:mldecoder}
\hat{\cbf}_{\text{ML}} = \underset{\cbf \in \calC}{\operatorname{argmin}}\;\| \ybf - \cbf \|^2,
%\hat{\cbf} &=& \mbox{arg~}\min_{\cbf \in \calC} \| \ybf - \cbf \|^2.
\end{equation}
that is, the receiver computes the codeword in $\calC$ nearest in Euclidean distance to the received signal $\ybf$.  Assuming that each codeword is transmitted with equal probability, then the probability of correct maximum likelihood decoding is
\[
P_{\text{ML}} = \frac{1}{\abs{\calC}}\sum_{\cbf \in \calC}\prob( \hat{\cbf}_{\text{ML}} = \cbf ).
\]

@@

This theorem asserts that the Voronoi cell of the lattice $A_n$ is the $n$-dimensional polytope that results from orthogonally projecting the $(n+1)$-dimensional hypercube into the zero-sum plane.  Results of this type have been studied previously.  A polytope that is the orthogonal projection of a hypercube is called a \emph{zonotope}~\cite[p.~313]{surveys_combin_zonotopes_1997}~\cite{McMullen_space_tiling_zonotopes_1975}.  Figure~\ref{fig:cuberothex} depicts some 2-dimensional zonotopes.  A zonotope is \emph{unimodular} if it can be used to tile (or tesselate) Euclidean space.  Such a tesselation naturally gives rise to a lattice, a so called \emph{zonotopal lattice}~\cite{Vallentin_space_tiling_zonotope_2004}.  The lattice $A_n$ is a zonotopal lattice and the techniques in this paper can potentially be extended to other zonotopal lattices.

@@

We have observed the following property.  The formula for $M_n(m)$ appears to always be in the form
\[
\frac{p(n)}{(1+n)^{m-1/2} d}
\] 
where $p(n) = a_0 + a_1n + \dots a_{2m} n^{2m}$ is a polynomial of degree $2m$ and $d$ is a positive integer.  The following appears to be true
\[
\frac{d}{a_{2m}} = 12^m,
\]
that is, the integer in the denominator $d$ is equal to the highest order coefficient $a_{2m}$ of the numerator polynomial $p(n)$ multiplied by $12^m$.  This leads us to make the following conjecture about the moments of $A_n$ when the dimension $n$ gets large.

@@

@@
